A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-06-07 paper/paper.Rmd
figure 7

```{r compare-subsets, fig.cap = "Comparison of original and refreshed data: (A) highest grade completed, (B) experience and (C) log wages. Some difference in wages would be expected because the refreshed data is not inflation-adjusted, but the two sets are reasonably similar.", fig.width = 9, fig.height = 5, out.width = "100%", cache = FALSE}
```

>>>>

```{r compare-subsets, fig.cap = "Comparison of original and refreshed data: (A) highest grade completed, (B) experience and (C) log wages. Some difference in wages would be expected because the refreshed data is not inflation-adjusted, but the two sets are reasonably similar.", fig.width = 9, fig.height = 4, out.width = "100%", cache = FALSE}
```
